Target Markdown

### 2023-08-22 _targets.Rmd

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes"
                            ))

@@

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
      tar_target(final_data, refine_data(matching, db_path, ids_complete, sup_control, authors_arrow)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data, authors_arrow, text_arrow)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector, authors_arrow)),
     tar_target(random_pubs,
           get_random_pubs(db_path, authors_arrow, text_arrow))
)
```

@@

    tar_target(independent_topics,
                comp_ind_topics(independent_pubs, topic_model, db_path, authors_arrow))
)

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes",
                            "cobalt",
                            "furrr"
                            ))

@@

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_manual_sup_search"),
      paths = here::here("data", "raw", "manual_sup_search.csv")),
  tarchetypes::tar_download(sup_path_second,
      urls = Sys.getenv("link_to_manual_sup_search_second"),
      paths = here::here("data", "raw", "manual_sup_search_second.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(name = db_path, 
                command = transcribe_database(path = here::here("data",
                                                                "raw",
                                                                "czech_sci_db.sqlite"),
                                              authors_arrow, 
                                              cep_investigators_arrow,   
                                              cep_details_arrow, 
                                              riv_details_arrow, 
                                              riv_authors_arrow,
                                              text_arrow),
                format = "file"
                )

@@

     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),

       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
      tar_target(sup_control_second, read.csv2(sup_path_second)),
      tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),

      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
     tar_target(random_pubs,
           get_random_pubs(db_path))
)
```

@@

    tar_target(independent_topics,
                comp_ind_topics(independent_pubs, topic_model, db_path))
)
